API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
trim grid search/randomized search section
The description of randomized search was far too long for a section
that is supposed to discuss APIs, not implementation.

@amueller, @mblondel, please check if it's still correct.

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as input an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
hyper-parameter grid, which defines the values to search. Optionally, they can
also take a cross-validation scheme and a score function.  The library provides
various such cross-validation schemes, including $k$-fold (default),
leave-one-out and iterated shuffled $k$-folds with optional sub-sampling.
The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a large variety of
score functions that the user can choose from,
including accuracy, AUC, $F_1$ score (classification),
$R^2$ score and mean squared error (regression).

\texttt{GridSearchCV} and \texttt{RandomizedSearchCV} differ in the way they
search the hyper-parameter grid.  \texttt{GridSearchCV} exhaustively searches
for all hyper-parameter combinations from the grid. This scheme can be expensive
when there are many possible hyper-parameter combinations.
\texttt{RandomizedSearchCV}, on the other hand, only searches for a limited
number of combinations, randomly sampled from the grid. Such scheme has been
shown to work well in practice while considerably reducing the computational
cost \citep{bergstra2012}. For each hyper-parameter combination and each train /
validation split generated by the cross-validation scheme, \texttt{GridSearchCV}
and \texttt{RandomizedSearchCV} fit the base estimator on the training set and
evaluate its performance on the validation set.  In the end, the best performing
model on average is retained and exposed as the public attribute
\texttt{best\_estimator\_}.

>>>>

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as input an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
set of hyperparameter settings to search through.
This set is represented as a mapping of parameter names
to a set of discrete choices in the case of grid search,
which exhaustively enumerates the ``grid'' (cartesian product)
of complete parameter choices.
Randomized search is a smarter algorithm
that avoids the combinatorial explosion in grid search
by sampling a fixed number of times from its parameter distributions
(see \citealt{bergstra2012}).
The rest of this section focuses mostly on grid search for simplicity.

Optionally, the model selection algorithms
also take a cross-validation scheme and a score function.  \sklearn provides
various such cross-validation schemes, including $k$-fold (default),
leave-one-out and iterated shuffled $k$-folds with optional sub-sampling.
The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a large variety of
score functions that the user can choose from,
including accuracy, AUC, $F_1$ score (classification),
$R^2$ score and mean squared error (regression).

For each hyper-parameter combination and each train/validation split
generated by the cross-validation scheme, \texttt{GridSearchCV}
and \texttt{RandomizedSearchCV} fit their base estimator on the training set and
evaluate its performance on the validation set.  In the end, the best performing
model on average is retained and exposed as the public attribute
\texttt{best\_estimator\_}.
